\singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant reproductive traits determine interactions with floral visitors

### 2021-10-06 Manuscript/Manuscript.Rmd
edits

Several studies have identified links between plant traits and plant-pollinator network properties [@bartomeus2013; @olito2015; @rowe2020]. Moreover, plant traits can also define species' network roles (@lazaro2013; @tur2013)(e.g., specialists vs generalists). For example, species that occupy trait space extremes are more likely to exhibit higher specialization and be more reliant on trait-matching [@junker2013; @coux2016]. This morphological matching between plant and floral visitors can determine plant-pollinator interactions, and thus shape their interaction network structure [@stang2009; @ibanez2012]. Remarkably, the combination of traits have shown to increase the predictive power of the network interactions [@eklof2013]. Therefore, considering the different plant reproductive trade-offs which represent the species strategy within the network [@dehling2016] could progress our understanding of plant-pollinator interactions. Further, we know little if the different network patterns generally studied at the community level are maintained when we scale up at macroecological scale.

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10,fig.align='center',fig.width=10,fig.cap= "**Fig. 1 | Plant life-history strategies.** Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies. The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation. The length of the arrows indicate the weight of the variables on each principal component and the dashed lines show the opposed direction of trait variation. The icons at both ends of arrows and dashed lines illustrate the extreme form of the trait continuum."}

@@

**Visitation patterns.** The main axes of trait variation explained little of the overall visitation rates ($conditional R2 = 0.31$; $marginal R2 = 0.06$) but showed relevant trends when we explored the interaction with the different floral visitor guilds (Fig. 3). All floral visitor guilds visited plant species with higher pollinator dependence more frequently (PC2; Fig. 3b and Fig. 3e). In addition, all guilds other than Syrphids and Lepidoptera (i.e., all Hymenoptera, non-Syrphidae-Diptera and Coleoptera) showed greater visitation rates on species with small numerous flowers (PC1; Fig. 3a and Fig. 3d). On the style length trade-off (PC3), Anthophila-Hymenoptera, Lepidoptera and Non-Anthophila-Hymenoptera showed greater visitation rates on plant species with larger styles and higher levels of selfing; while Syrphidae, Non-Syrphidae-Diptera and Coleoptera showed higher visitation rates on species with shorter styles and lower selfing (Fig. 3c and Fig. 3f). Furthermore, when running an additional model that separates the most represented families of Anthophila-Hymenoptera (bees; $marginal R2 = 0.30$; $conditional R2 = 0.03$) showed that the family Apidae was the main driver of the observed patterns (Supplementary Fig. S8).

@@

Here, we show that plant species exhibit clear trade-offs in their floral, reproductive biology and vegetative traits. These trade-offs are differentiated on three main axes of trait variation: (i) flower number - flower size, (ii) pollinator dependence and (iii) style length. Although these axes of trait variation did not explain overall visitation rates, we found that plant life strategies were clearly associated with different floral visitor guilds. Interestingly, pollen and nectar related traits were better than all other traits for characterizing plant species functional roles within their interaction networks.

@@

Despite the low predictive power of the main axes of trait variation on overall visitation patterns, we found commonalities among and within floral visitors guilds across these axes that indicate the influence of life-history strategies on floral visitation rate. For example, all guilds showed an increasing trend of visitation on plant species with higher pollinator dependence, which were also associated with larger floral displays and greater pollen quantities (Fig. 1 and Supplementary Fig. S6). This trend is consistent with previous plant-pollinator studies that show higher visitation rates on species that make greater reproductive investment [@hegland2005; @lazaro2013; @kaiser2014]. In regard to the flower number - flower size and style length trade-offs, different guilds showed contrasting visitation rates, which could be associated with different pollination syndromes at a macroecological scale. For instance, the guilds of bees and syrphids were clearly associated with opposing life-strategies on PC1 and PC3 (Fig. 3) indicating a possible niche partitioning among these two guilds [@palmer2003; @phillips2020]. However, these plant-pollinator associations do not account for some of the traits (i.e., pollen and nectar quantity) that had greater relevance on the species network roles (Fig. 4) because of insufficient data availability and lack of pollinator efficiency measurements for more complete descriptions of the pollination syndromes [@dellinger2020]. In any case, it is worth noting that this general pattern emerges in field-measured plant-pollinator networks, where other local factors such as species relative abundances, will surely explain part of the observed variability [@vazquez2007; @encinas2012; @bartomeus2016].

>>>>

Several studies have identified links between plant traits and plant-pollinator network properties [@bartomeus2013; @olito2015; @rowe2020]. Moreover, plant traits can also define species' network roles [@lazaro2013; @tur2013] (e.g., specialists vs generalists). For example, species that occupy trait space extremes are more likely to exhibit higher specialization and be more reliant on trait-matching [@junker2013; @coux2016]. This morphological matching between plant and floral visitors can determine plant-pollinator interactions, and thus shape their interaction network structure [@stang2009; @ibanez2012]. Remarkably, the combination of traits have shown to increase the predictive power of the network interactions [@eklof2013]. Therefore, considering the different plant reproductive trade-offs which represent the species strategy within the network [@dehling2016] could progress our understanding of plant-pollinator interactions. Further, we know little if the different network patterns generally studied at the community level are maintained when we scale up at macroecological scale.

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10,fig.align='center',fig.width=10,fig.cap= "\\textbf{Fig. 1 | Plant life-history strategies.} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies. The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation. The length of the arrows indicate the weight of the variables on each principal component and the dashed lines show the opposed direction of trait variation. The icons at both ends of arrows and dashed lines illustrate the extreme form of the trait continuum."}

@@

**Visitation patterns.** The main axes of trait variation explained partly presence-absence interactions between plant and floral visitors ($conditional R2 = 0.26$; $marginal R2 = 0.20$) but little of the overall visitation rates ($conditional R2 = 0.31$; $marginal R2 = 0.06$). However, we found relevant trends across the different floral visitor guilds on both presence-absence and visitation interactions (Fig. 3). On the pollinator dependence trade-off, all floral visitor guilds interacted more frequently with plant species with higher pollinator dependence (PC2; Fig. 3b and Fig. 3e). For presence-absence interactions we found that all Diptera, Coleoptera and non-bee Hymenoptera guilds interacted more frequently with plants with high flower number and small flowers (flower number - flower size trade-off, PC1; Fig. 3a) but bees and Lepidoptera interacted slightly more frequently with plant species with low flower number but large flowers. For presence-absence interactions on PC3 (style length trade-off; Fig. 3c), we found that bees interacted clearly more with plant species with long styles and high selfing and the rest of the guilds interacted slightly more with plant species with short styles and low selfing. In addition, all guilds other than Syrphids and Lepidoptera (i.e., all Hymenoptera, non-Syrphidae-Diptera and Coleoptera) showed greater visitation rates on species with small numerous flowers (PC1; Fig. 3d). On the style length trade-off, bees, Lepidoptera and Non-Anthophila-Hymenoptera showed greater visitation rates on plant species with larger styles and higher levels of selfing; while Syrphidae, Non-Syrphidae-Diptera and Coleoptera showed higher visitation rates on species with shorter styles and lower selfing (Fig. 3f).

The additional model for both presence-absence ($marginal R2 = 0.29$; $conditional R2 = 0.19$) and visitation rate ($marginal R2 = 0.30$; $conditional R2 = 0.03$) for the most represented families of bees showed that the family Apidae was the main driver of the observed patterns and that the contrasting differences between presence-absence and visitation rate for bees on PC1 (Fig. 3a and Fig. 3d) were driven by the family Andrenidae which interacted more frequently on presence-absence interactions with plant species with low number of flower but large (Supplementary Fig. S8).

@@

Here, we show that plant species exhibit clear trade-offs in their floral, reproductive biology and vegetative traits. These trade-offs are differentiated on three main axes of trait variation: (i) flower number - flower size, (ii) pollinator dependence and (iii) style length. These axes of trait variation explained partly the presence-absence interactions between plants and floral visitors but did not explain the overall visitation rates. However, on both qualitative and quantitative interactions floral visitor guilds showed associations with the different reproductive trade-offs. Interestingly, pollen and nectar related traits were better than all other traits for characterizing plant species functional roles within their interaction networks.

@@

Despite the low predictive power of the main axes of trait variation on overall interaction patterns (presence-absence and visitation rate), we found commonalities among and within floral visitors guilds across these axes that indicate the influence of life-history strategies on plant-pollinator interactions. For example, all guilds showed an increasing trend of visitation on plant species with higher pollinator dependence, which were also associated with larger floral displays and greater pollen quantities (Fig. 1 and Supplementary Fig. S6). This trend is consistent with previous plant-pollinator studies that show higher visitation rates on species that make greater reproductive investment [@hegland2005; @lazaro2013; @kaiser2014]. In regard to the flower number - flower size and style length trade-offs, different guilds showed contrasting visitation rates, which could be associated with different pollination syndromes at a macroecological scale. For instance, the guilds of bees and syrphids were clearly associated with opposing life-strategies on PC1 and PC3 (Fig. 3) indicating a possible niche partitioning among these two guilds [@palmer2003; @phillips2020]. However, these plant-pollinator associations do not account for some of the traits (i.e., pollen and nectar quantity) that had greater relevance on the species network roles (Fig. 4) because of insufficient data availability and lack of pollinator efficiency measurements for more complete descriptions of the pollination syndromes [@dellinger2020]. In any case, it is worth noting that this general pattern emerges in field-measured plant-pollinator networks, where other local factors such as species relative abundances, will surely explain part of the observed variability [@vazquez2007; @encinas2012; @bartomeus2016].

### 2021-10-06 Manuscript/Manuscript.tex
edits

Several studies have identified links between plant traits and
plant-pollinator network
properties\textsuperscript{\protect\hyperlink{ref-bartomeus2013}{33}--\protect\hyperlink{ref-rowe2020}{35}}.
Moreover, plant traits can also define species' network roles
(\protect\hyperlink{ref-lazaro2013}{36};
\protect\hyperlink{ref-tur2013}{20})(e.g., specialists vs generalists).
For example, species that occupy trait space extremes are more likely to
exhibit higher specialization and be more reliant on
trait-matching\textsuperscript{\protect\hyperlink{ref-junker2013}{37},\protect\hyperlink{ref-coux2016}{38}}.
This morphological matching between plant and floral visitors can
determine plant-pollinator interactions, and thus shape their
interaction network
structure\textsuperscript{\protect\hyperlink{ref-stang2009}{16},\protect\hyperlink{ref-ibanez2012}{39}}.
Remarkably, the combination of traits have shown to increase the
predictive power of the network
interactions\textsuperscript{\protect\hyperlink{ref-eklof2013}{40}}.
Therefore, considering the different plant reproductive trade-offs which
represent the species strategy within the
network\textsuperscript{\protect\hyperlink{ref-dehling2016}{14}} could
progress our understanding of plant-pollinator interactions. Further, we
know little if the different network patterns generally studied at the
community level are maintained when we scale up at macroecological
scale.

@@

\caption{**Fig. 1 | Plant life-history strategies.** Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies. The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation. The length of the arrows indicate the weight of the variables on each principal component and the dashed lines show the opposed direction of trait variation. The icons at both ends of arrows and dashed lines illustrate the extreme form of the trait continuum.}\label{fig:unnamed-chunk-1}
\end{figure}

@@

\textbf{Visitation patterns.} The main axes of trait variation explained
little of the overall visitation rates (\(conditional R2 = 0.31\);
\(marginal R2 = 0.06\)) but showed relevant trends when we explored the
interaction with the different floral visitor guilds (Fig. 3). All
floral visitor guilds visited plant species with higher pollinator
dependence more frequently (PC2; Fig. 3b and Fig. 3e). In addition, all
guilds other than Syrphids and Lepidoptera (i.e., all Hymenoptera,
non-Syrphidae-Diptera and Coleoptera) showed greater visitation rates on
species with small numerous flowers (PC1; Fig. 3a and Fig. 3d). On the
style length trade-off (PC3), Anthophila-Hymenoptera, Lepidoptera and
Non-Anthophila-Hymenoptera showed greater visitation rates on plant
species with larger styles and higher levels of selfing; while
Syrphidae, Non-Syrphidae-Diptera and Coleoptera showed higher visitation
rates on species with shorter styles and lower selfing (Fig. 3c and Fig.
3f). Furthermore, when running an additional model that separates the
most represented families of Anthophila-Hymenoptera (bees;
\(marginal R2 = 0.30\); \(conditional R2 = 0.03\)) showed that the
family Apidae was the main driver of the observed patterns
(Supplementary Fig. S8).

@@

Despite the low predictive power of the main axes of trait variation on
overall visitation patterns, we found commonalities among and within
floral visitors guilds across these axes that indicate the influence of
life-history strategies on floral visitation rate. For example, all
guilds showed an increasing trend of visitation on plant species with
higher pollinator dependence, which were also associated with larger
floral displays and greater pollen quantities (Fig. 1 and Supplementary
Fig. S6). This trend is consistent with previous plant-pollinator
studies that show higher visitation rates on species that make greater
reproductive
investment\textsuperscript{\protect\hyperlink{ref-lazaro2013}{36},\protect\hyperlink{ref-hegland2005}{44},\protect\hyperlink{ref-kaiser2014}{45}}.
In regard to the flower number - flower size and style length
trade-offs, different guilds showed contrasting visitation rates, which
could be associated with different pollination syndromes at a
macroecological scale. For instance, the guilds of bees and syrphids
were clearly associated with opposing life-strategies on PC1 and PC3
(Fig. 3) indicating a possible niche partitioning among these two
guilds\textsuperscript{\protect\hyperlink{ref-palmer2003}{46},\protect\hyperlink{ref-phillips2020}{47}}.
However, these plant-pollinator associations do not account for some of
the traits (i.e., pollen and nectar quantity) that had greater relevance
on the species network roles (Fig. 4) because of insufficient data
availability and lack of pollinator efficiency measurements for more
complete descriptions of the pollination
syndromes\textsuperscript{\protect\hyperlink{ref-dellinger2020}{4}}. In
any case, it is worth noting that this general pattern emerges in
field-measured plant-pollinator networks, where other local factors such
as species relative abundances, will surely explain part of the observed
variability\textsuperscript{\protect\hyperlink{ref-bartomeus2016}{17},\protect\hyperlink{ref-vazquez2007}{48},\protect\hyperlink{ref-encinas2012}{49}}.

@@

\hypertarget{ref-sargent2008}{}
10. Sargent, R. D. \& Ackerly, D. D. Plant--pollinator interactions and
the assembly of plant communities. \emph{Trends in Ecology \& Evolution}
\textbf{23}, 123--130 (2008).

\hypertarget{ref-rech2016}{}
11. Rech, A. R. \emph{et al.} The macroecology of animal versus wind
pollination: Ecological factors are more important than historical
climate stability. \emph{Plant Ecology \& Diversity} \textbf{9},
253--262 (2016).

@@

\hypertarget{ref-dehling2016}{}
14. Dehling, D. M., Jordano, P., Schaefer, H. M., Böhning-Gaese, K. \&
Schleuning, M. Morphology predicts species' functional roles and their
degree of specialization in plant--frugivore interactions.
\emph{Proceedings of the Royal Society B: Biological Sciences}
\textbf{283}, 20152444 (2016).

\hypertarget{ref-rosas2014}{}
15. Rosas-Guerrero, V. \emph{et al.} A quantitative review of
pollination syndromes: Do floral traits predict effective pollinators?
\emph{Ecology letters} \textbf{17}, 388--400 (2014).

@@

\hypertarget{ref-laughlin2021}{}
28. Laughlin, D. C. \emph{et al.} Root traits explain plant species
distributions along climatic gradients yet challenge the nature of
ecological trade-offs. \emph{Nature Ecology \& Evolution} 1--12 (2021).

@@

\hypertarget{ref-eklof2013}{}
40. Eklöf, A. \emph{et al.} The dimensionality of ecological networks.
\emph{Ecology letters} \textbf{16}, 577--583 (2013).

@@

\hypertarget{ref-healy2019}{}
43. Healy, K., Ezard, T. H. G., Jones, O. R., Salguero-Gómez, R. \&
Buckley, Y. M. Animal life history is shaped by the pace of life and the
distribution of age-specific mortality and reproduction. \emph{Nat.
Ecol. Evol} \textbf{3}, 1217--1224 (2019).

>>>>

Several studies have identified links between plant traits and
plant-pollinator network
properties\textsuperscript{\protect\hyperlink{ref-bartomeus2013}{33}--\protect\hyperlink{ref-rowe2020}{35}}.
Moreover, plant traits can also define species' network
roles\textsuperscript{\protect\hyperlink{ref-tur2013}{20},\protect\hyperlink{ref-lazaro2013}{36}}
(e.g., specialists vs generalists). For example, species that occupy
trait space extremes are more likely to exhibit higher specialization
and be more reliant on
trait-matching\textsuperscript{\protect\hyperlink{ref-junker2013}{37},\protect\hyperlink{ref-coux2016}{38}}.
This morphological matching between plant and floral visitors can
determine plant-pollinator interactions, and thus shape their
interaction network
structure\textsuperscript{\protect\hyperlink{ref-stang2009}{16},\protect\hyperlink{ref-ibanez2012}{39}}.
Remarkably, the combination of traits have shown to increase the
predictive power of the network
interactions\textsuperscript{\protect\hyperlink{ref-eklof2013}{40}}.
Therefore, considering the different plant reproductive trade-offs which
represent the species strategy within the
network\textsuperscript{\protect\hyperlink{ref-dehling2016}{14}} could
progress our understanding of plant-pollinator interactions. Further, we
know little if the different network patterns generally studied at the
community level are maintained when we scale up at macroecological
scale.

@@

\caption{\textbf{Fig. 1 | Plant life-history strategies.} Phylogenetically informed principal component analysis (pPCA) of 1,236 plant species from 28 plant-pollinator network studies. The solid arrows indicate the direction of the different quantitative traits (flower number, plant height, style length, flower size, ovule number and level of autonomous selfing) across the two main axes of trait variation. The length of the arrows indicate the weight of the variables on each principal component and the dashed lines show the opposed direction of trait variation. The icons at both ends of arrows and dashed lines illustrate the extreme form of the trait continuum.}\label{fig:unnamed-chunk-1}
\end{figure}

@@

\textbf{Visitation patterns.} The main axes of trait variation explained
partly presence-absence interactions between plant and floral visitors
(\(conditional R2 = 0.26\); \(marginal R2 = 0.20\)) but little of the
overall visitation rates (\(conditional R2 = 0.31\);
\(marginal R2 = 0.06\)). However, we found relevant trends across the
different floral visitor guilds on both presence-absence and visitation
interactions (Fig. 3). On the pollinator dependence trade-off, all
floral visitor guilds interacted more frequently with plant species with
higher pollinator dependence (PC2; Fig. 3b and Fig. 3e). For
presence-absence interactions we found that all Diptera, Coleoptera and
non-bee Hymenoptera guilds interacted more frequently with plants with
high flower number and small flowers (flower number - flower size
trade-off, PC1; Fig. 3a) but bees and Lepidoptera interacted slightly
more frequently with plant species with low flower number but large
flowers. For presence-absence interactions on PC3 (style length
trade-off; Fig. 3c), we found that bees interacted clearly more with
plant species with long styles and high selfing and the rest of the
guilds interacted slightly more with plant species with short styles and
low selfing. In addition, all guilds other than Syrphids and Lepidoptera
(i.e., all Hymenoptera, non-Syrphidae-Diptera and Coleoptera) showed
greater visitation rates on species with small numerous flowers (PC1;
Fig. 3d). On the style length trade-off, bees, Lepidoptera and
Non-Anthophila-Hymenoptera showed greater visitation rates on plant
species with larger styles and higher levels of selfing; while
Syrphidae, Non-Syrphidae-Diptera and Coleoptera showed higher visitation
rates on species with shorter styles and lower selfing (Fig. 3f).

The additional model for both presence-absence (\(marginal R2 = 0.29\);
\(conditional R2 = 0.19\)) and visitation rate (\(marginal R2 = 0.30\);
\(conditional R2 = 0.03\)) for the most represented families of bees
showed that the family Apidae was the main driver of the observed
patterns and that the contrasting differences between presence-absence
and visitation rate for bees on PC1 (Fig. 3a and Fig. 3d) were driven by
the family Andrenidae which interacted more frequently on
presence-absence interactions with plant species with low number of
flower but large (Supplementary Fig. S8).

@@

Despite the low predictive power of the main axes of trait variation on
overall interaction patterns (presence-absence and visitation rate), we
found commonalities among and within floral visitors guilds across these
axes that indicate the influence of life-history strategies on
plant-pollinator interactions. For example, all guilds showed an
increasing trend of visitation on plant species with higher pollinator
dependence, which were also associated with larger floral displays and
greater pollen quantities (Fig. 1 and Supplementary Fig. S6). This trend
is consistent with previous plant-pollinator studies that show higher
visitation rates on species that make greater reproductive
investment\textsuperscript{\protect\hyperlink{ref-lazaro2013}{36},\protect\hyperlink{ref-hegland2005}{44},\protect\hyperlink{ref-kaiser2014}{45}}.
In regard to the flower number - flower size and style length
trade-offs, different guilds showed contrasting visitation rates, which
could be associated with different pollination syndromes at a
macroecological scale. For instance, the guilds of bees and syrphids
were clearly associated with opposing life-strategies on PC1 and PC3
(Fig. 3) indicating a possible niche partitioning among these two
guilds\textsuperscript{\protect\hyperlink{ref-palmer2003}{46},\protect\hyperlink{ref-phillips2020}{47}}.
However, these plant-pollinator associations do not account for some of
the traits (i.e., pollen and nectar quantity) that had greater relevance
on the species network roles (Fig. 4) because of insufficient data
availability and lack of pollinator efficiency measurements for more
complete descriptions of the pollination
syndromes\textsuperscript{\protect\hyperlink{ref-dellinger2020}{4}}. In
any case, it is worth noting that this general pattern emerges in
field-measured plant-pollinator networks, where other local factors such
as species relative abundances, will surely explain part of the observed
variability\textsuperscript{\protect\hyperlink{ref-bartomeus2016}{17},\protect\hyperlink{ref-vazquez2007}{48},\protect\hyperlink{ref-encinas2012}{49}}.

@@

\hypertarget{ref-sargent2008}{}
10. Sargent, R. D. \& Ackerly, D. D. Plant--pollinator interactions and
the assembly of plant communities. \emph{Trends Ecol. Evol.}
\textbf{23}, 123--130 (2008).

\hypertarget{ref-rech2016}{}
11. Rech, A. R. \emph{et al.} The macroecology of animal versus wind
pollination: Ecological factors are more important than historical
climate stability. \emph{Plant Ecol. Divers.} \textbf{9}, 253--262
(2016).

@@

\hypertarget{ref-dehling2016}{}
14. Dehling, D. M., Jordano, P., Schaefer, H. M., Böhning-Gaese, K. \&
Schleuning, M. Morphology predicts species' functional roles and their
degree of specialization in plant--frugivore interactions. \emph{Proc.
Royal Soc. B} \textbf{283}, 20152444 (2016).

\hypertarget{ref-rosas2014}{}
15. Rosas-Guerrero, V. \emph{et al.} A quantitative review of
pollination syndromes: Do floral traits predict effective pollinators?
\emph{Ecol. Lett.} \textbf{17}, 388--400 (2014).

@@

\hypertarget{ref-laughlin2021}{}
28. Laughlin, D. C. \emph{et al.} Root traits explain plant species
distributions along climatic gradients yet challenge the nature of
ecological trade-offs. \emph{Nat. Ecol. Evol.} 1--12 (2021).

@@

\hypertarget{ref-eklof2013}{}
40. Eklöf, A. \emph{et al.} The dimensionality of ecological networks.
\emph{Ecol. Lett.} \textbf{16}, 577--583 (2013).

@@

\hypertarget{ref-healy2019}{}
43. Healy, K., Ezard, T. H. G., Jones, O. R., Salguero-Gómez, R. \&
Buckley, Y. M. Animal life history is shaped by the pace of life and the
distribution of age-specific mortality and reproduction. \emph{Nat.
Ecol. Evol.} \textbf{3}, 1217--1224 (2019).
